### 2018-01-13 ident/docs/ident_manuscript.tex
additions to sec 3.1

We believe this problem of computational tractability will occur in other complex kinetic rate law formulations as well. Example?

>>>>

We believe that this is not a unique problem isolated to the system that we are investigating. Complicated expressions for describing fluxes have been extensively used to model observed experimental data for different fluxes in a variety of organisms (Chassagnole, other yeast and e. coli kinetic modeling papers). However, the identifiability of the parameters used in these models has never been truly examined. Any test for identifiability is forgone in favor of direct parameter estimation using a nonlinear least squares optimization approach with powerful computers to overcome difficulties associated with getting global optimal solutions (). This is however paving way for probabilistic approaches based on Bayesian techniques (Lars Nielsen papers). Furthermore none of these methods address the issue of designing experiments to suit parameter estimation. Parameter estimation for kinetic models has always focused on the ability to estimate parameters from existing data without the need for additional experiments, which might not be always possible if parameters are not identifiable from existing experimental data.

We believe this problem of computational tractability will occur in other complex kinetic rate law formulations as well. Example(s)?
